---
title: "Flanker: a tool for comparative genomics of gene flanking regions"
author: "Will Matlock and Sam Lipworth"
date: "26/01/2021"
output: html_document

---

```{r fig options,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
knitr::opts_chunk$set(fig.width=15, fig.height=30) 
```



This R markdown script accompanies the manuscript "Flanker: a tool for comparative genomics of gene flanking regions" (Matlock/Lipworth et al 2021).
Work through the code chunks sequentially or you can knit it.
Any issues/questions please email samuel.lipworth@ndm.ox.ac.uk (wrote this R code) or william.matlock@wadham.ox.ac.uk / twitter @samlipworth @wtmatlock

Essentially we do three things:
1) take flanker output and classify Flank Patterns (Overall pattern over all window clusters)
2) plot a mashtree of plasmid assemblies
3) plot an schematic alignment of genes using gggenes

We then slot all these together in a facet plot and add some info on presence/absence of plasmids as called by Plasmidfinder. 

This should be generally useful for anyone wanting to take Prokka output and plot an alignment against a tree.



```{r libraries, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(ape)
library(igraph)
library(phytools)
library(ggtree)
library(genbankr)
library(gggenes)
library(ggnewscale)
library(RColorBrewer)
library(gtable)
library(grid)
library(kableExtra)


```

```{r KPC Flanker, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#here we take the output from Flanker. the 'all' file is created simply with cat [outprefix e.g. -o out]* | sed '/assembly/d' > all 
#The add the headers isolate,group to the 'all' csv
flanker_output<-read_csv('./kpc/all')

#here we just parse some messy filenames - you might need to adjust or be able to omit this
flanker_output<-flanker_output %>% 
  mutate(window = map_chr(isolate, function(s) rev(strsplit(s, "_")[[1]])[3]))

flanker_output$window<-as.numeric(flanker_output$window)
x<-unique(flanker_output$window) %>% sort()
flanker_output<-flanker_output %>% 
  mutate(guuid = map_chr(isolate, function(s) rev(strsplit(s, "_")[[1]])[6]))

flanker_output<-flanker_output %>% 
  mutate(gene = map_chr(isolate, function(s) rev(strsplit(s, "_")[[1]])[5]))

gene<-select(flanker_output,guuid,gene)
flanker_output<-select(flanker_output,guuid,window,group)
#go from long to wide
flanker_output<-flanker_output %>% pivot_wider(id_cols = guuid,names_from=window,values_from=group,names_sort=TRUE)

#give an ID based on the pattern over all 72 windows (7200/100)
flanker_output$ID<-flanker_output %>% group_indices(flanker_output[,2:73])

#take the ids and add them back to the long format for plotting
test<-select(flanker_output,guuid,ID) %>% distinct()

flanker_output<-select(flanker_output,-ID)
flanker_output<-flanker_output %>% pivot_longer(-guuid,names_to = "window",values_to="group")

flanker_output<-left_join(flanker_output,test,by=c("guuid"="guuid"))


flanker_output$window<-as.numeric(flanker_output$window)
flanker_output<-left_join(flanker_output,gene,by=c("guuid"="guuid"))
kpc_store<-flanker_output # we'll use this later
```

```{r KPC plasmid tree, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#read in a mashtree of plasmid fastas e.g. mashtree *_plasmid.fasta --outtree tree.tree
tree<-read.tree('./kpc/tree.tree')
tree<-midpoint.root(tree)
x<-data.frame(tree$tip.label)
#sort out messy names again
x<-x %>% 
  mutate(id = map_chr(tree.tip.label, function(s) rev(strsplit(s, "_")[[1]])[1]))

tree$tip.label<-x$id
x<-left_join(x,gene,by=c("id"="guuid"))
x<-select(x,id,gene) %>% distinct()

g<-ggtree(tree)
p1<- g %<+% x + geom_tippoint(aes(color=gene)) + geom_tiplab()

#here is our first plot of the flankergram and tree - we colour the tiplabels by gene 

px<-p1 + geom_facet(panel="flankergram", data=flanker_output,aes(x=window,fill=group), geom=geom_tile) 
names(flanker_output)<-c('id','window','group','cluster','gene')


#read in a file with mlst data
mlst<-read_csv('~/kpc/mlst.csv') #%>% select(guuid,mlst)


```

```{r KPC gene alignemnt, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#all .gbk files in one directory
#n.b. if you make these with prokka, you MUST use the --compliant option
filenames<-list.files("./kpc/",pattern="*.gbk",full.names = TRUE)
filenames<-str_replace_all(filenames,'//','/')
files<-as.list(filenames)


files2<-lapply(files, readGenBank)

#here we parse prokka genbank files into a nice dataframe for plotting
for (i in 1:length(files2)){
  assign(paste(paste("df", i, sep="_"), "summary", sep="."), data.frame(genes(files2[[i]])))
  t<-paste(paste("df", i, sep="_"), "summary", sep=".")
  df<-get(t)
  df$seqnames<-paste('g',i,sep='')
  assign(paste(paste("df", i, sep="_"), "summary", sep="."), df)
}

files2<-lapply(ls(pattern='df_*'), get)

gggene_configure<-function(seqname){
  seqname<-select(seqname,seqnames,gene,start,end,strand)
  seqname$gene<-ifelse(is.na(seqname$gene),'hypothetical',seqname$gene)
  seqname$strand<-ifelse(seqname$strand=='+','forward','reverse')
  seqname$direction<-ifelse(seqname$strand =='forward',1,-1)

  return(seqname)
  
}

dfs<-lapply(ls(pattern = 'df_'),get)


all<-bind_rows(dfs)
all2<-gggene_configure(all)
all<-all2
all<-select(all,seqnames,gene,start,end,strand,direction)
names(all)<-c('molecule','gene','start','end','strand','direction')
filenames<-data.frame(filenames)
filenames<-filenames %>% 
  mutate(isolate = map_chr(filenames, function(s) rev(strsplit(s, "_")[[1]])[6])) 
filenames$isolate<-str_replace_all(filenames$isolate,'.gbk','')
filenames<-select(filenames,-filenames)
filenames$molecule<-paste('g',1:nrow(filenames),sep = '')

filenames$isolate<-str_replace_all(filenames$isolate,'^.*/','')

all<-left_join(all,filenames,by=c("molecule"="molecule"))
all<-select(all,isolate,gene,start,end,strand,direction)
names(all)<-c('id','gene','start','end','strand','direction')

FP<-filter(flanker_output,window==7200) %>% distinct() %>% select(id,cluster)
all<-left_join(all,FP,by=c("id"="id"))
all$gene<-ifelse(all$gene=='bla','bla',paste('FP',all$cluster,sep=''))



#let's plot the gene alignment - check it looks OK
g<-ggplot(all,aes(xmin=start,xmax=end,y=id,fill=gene,forward=direction)) +
  geom_gene_arrow() + theme_genes() 




g<-ggtree(tree)

y<-select(x,id)

plasmids<-read_tsv('~/kpc/plasmids') %>% filter(id >=80 & cov >= 80) %>% select(guuid,gene)
plasmids$Present='Present'

c<-plasmids %>% group_by(gene) %>% count() %>% filter(n >=4)
plasmids<-filter(plasmids,gene %in% c$gene)

plasmids$guuid<-str_replace_all(plasmids$guuid,'^.*_','')

names(plasmids)<-c('id','gene','present')
plasmids<-left_join(y,plasmids,by=c("id"="id"))

plasmids<-pivot_wider(plasmids,names_from  = gene,id_cols  = id,values_from = present)
plasmids$`IncFIB(pQil)_1_pQil`<-ifelse(is.na(plasmids$`IncFIB(pQil)_1_pQil`),'absent','present')
plasmids$IncFII_1_pKP91<-ifelse(is.na(plasmids$IncFII_1_pKP91),'absent','present')
plasmids$`IncFIB(K)_1_Kpn3`<-ifelse(is.na(plasmids$`IncFIB(K)_1_Kpn3`),'absent','present')
plasmids$IncX3_1<-ifelse(is.na(plasmids$IncX3_1),'absent','present')

t<-c( "#FFFFFF", "#000000")

p1<-facet_plot(g, panel = "FIB(pQil)-type",data=plasmids,geom=geom_tile,aes(x=1,fill=`IncFIB(pQil)_1_pQil`)) + scale_fill_manual(values=t)

p2<-facet_plot(p1, panel = "FII(pKP91)-type",data=plasmids,geom=geom_tile,aes(x=1,fill=`IncFII_1_pKP91`)) + scale_fill_manual(values=t)

p3<-facet_plot(p2, panel = "FIB(Kpn3)-type",data=plasmids,geom=geom_tile,aes(x=1,fill=`IncFIB(K)_1_Kpn3`)) + scale_fill_manual(values=t,name="Plasmid Present?")

p3<-p3 + new_scale_fill()



gene_kpc<-read_tsv('~/kpc/KPC_presence')

t<-c("#41963E" ,"#792194")
gene_kpc<-gene_kpc %>% 
  mutate(id = map_chr(id, function(s) rev(strsplit(s, "_")[[1]])[6]))

p3<-p3 + new_scale_fill()
p4<-facet_plot(p3, panel = "Gene",data=gene_kpc,geom=geom_tile,aes(x=1,fill=gene)) + scale_fill_manual(values=t,name="Gene")

mycolors <- colorRampPalette(brewer.pal(9, "Set1"))(10)
p4<-p4 + new_scale_fill()

p5<-p4 + geom_facet(panel = 'Alignment',mapping= aes(xmin=start,xmax=end,fill=gene,forward=direction),
                     data = all, geom = geom_motif, on = 'bla') + scale_fill_manual(values = mycolors,breaks=c("FP1","FP2","FP3","FP4","FP5","FP6","FP7","FP8","FP9"),name='Flank Pattern')

p5<-p5 + new_scale_fill()
flanker_output$window<-flanker_output$window * -1
p6<-facet_plot(p5, panel="Flankergram",data=flanker_output,geom=geom_tile, aes(x=window,fill=group)) + scale_fill_viridis_c(name='Window Cluster')

p6<-p6 +new_scale_fill()

mlst<-read_csv('~/kpc/mlst.csv')
m<-mlst %>% group_by(mlst) %>% count() %>% filter(n>1)
mlst$mlst<-ifelse(mlst$mlst %in% m$mlst, mlst$mlst,'other')

mycolors <- colorRampPalette(brewer.pal(9, "Set1"))(10)

p7<-facet_plot(p6,panel="MLST",data=mlst,geom=geom_tile,aes(x=1,fill=mlst)) + scale_fill_manual(values=mycolors,name='MLST')





p8<- p7 + theme_bw() +
  xlim_tree(0.08) +
  xlim_expand(c(-7200,0),'Alignment') +
  xlim_expand(c(-7200,0),'Flankergram') + 
  theme(axis.text.y = element_blank(),axis.ticks.y = element_blank()) +
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black')) +
  theme(strip.text = element_text(size=16)) +
  theme(axis.text.x = element_text(size=14)) +
  theme(legend.text = element_text(size=16)) +
  theme(legend.title = element_text(size=16))



#have to make mlst/flank panels smaller
gt = ggplot_gtable(ggplot_build(p8))
gtable_show_layout(gt) # will show you the layout - very handy function
gt # see plot layout in table format
gt$layout$l[grep('panel-1-2', gt$layout$name)] # you want to find the column specific to panel-2
gt$widths[9] = 0.3*gt$widths[9] # in this case it was colmun 7 - reduce the width by a half
gt$widths[7] = 0.3*gt$widths[7]
gt$widths[11] = 0.3*gt$widths[11]
gt$widths[13] = 0.3*gt$widths[13]
gt$widths[19] = 0.3*gt$widths[19]

grid.draw(gt) # plot with grid draw

```

```{r OXA Flanker output, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

#and we do the same thing (basically) all over again for OXA
flanker_output<-read_csv('./oxa/all') 
flanker_output<-flanker_output %>% mutate(window = map_chr(isolate, function(s) rev(strsplit(s, "_")[[1]])[3])) 
flanker_output$window<-as.numeric(flanker_output$window) 

x<-unique(flanker_output$window) %>% sort() 
flanker_output<-flanker_output %>% mutate(guuid = map_chr(isolate, function(s) rev(strsplit(s, "_")[[1]])[6]))

flanker_output<-flanker_output %>% mutate(gene = map_chr(isolate, function(s) rev(strsplit(s, "_")[[1]])[5])) 

gene<-select(flanker_output,guuid,gene)
flanker_output<-select(flanker_output,guuid,window,group) 
flanker_output<-flanker_output %>% pivot_wider(id_cols = guuid,names_from=window,values_from=group,names_sort=TRUE) 

#23 because in the paper the Flank Pattern is over 2200bp (first column is isolate name)
flanker_output$ID<-flanker_output %>% group_indices(flanker_output[,2:23]) 
test<-select(flanker_output,guuid,ID) %>% distinct() 

flanker_output<-select(flanker_output,-ID) 
flanker_output<-flanker_output %>% pivot_longer(-guuid,names_to = "window",values_to="group")

flanker_output<-left_join(flanker_output,test,by=c("guuid"="guuid")) 
flanker_output$window<-as.numeric(flanker_output$window) 
flanker_output<-left_join(flanker_output,gene,by=c("guuid"="guuid")) 


#just check this looks sensible
p0<-ggplot(flanker_output) + aes(x=window,y=interaction(guuid,ID),fill=group) +geom_tile() + theme_minimal() + facet_wrap(~gene) 

```

```{r OXA plasmid tree, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#here should be your mashtree of plasmids
tree<-read.tree('./oxa/tree.tree')
tree<-midpoint.root(tree)
x<-data.frame(tree$tip.label)

x<-x %>% 
  mutate(id = map_chr(tree.tip.label, function(s) rev(strsplit(s, "_")[[1]])[1]))

tree$tip.label<-x$id

y<-unique(flanker_output$guuid)
pruned.tree<-drop.tip(tree,tree$tip.label[-match(y, tree$tip.label)])
tree<-pruned.tree
x<-left_join(x,gene,by=c("id"="guuid"))
x<-select(x,id,gene) %>% distinct()

g<-ggtree(tree)
p1<- g %<+% x + geom_tippoint(aes(color=gene))

names(flanker_output)<-c('id','window','group','cluster','gene')



```

```{r OXA gene alignment, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#make sure all gbk files in your working directory
filenames<-list.files("./oxa/",pattern="*.gbk",full.names = TRUE)
filenames<-str_replace_all(filenames,'./oxa//','./oxa/')
files<-as.list(filenames)


files2<-lapply(files, readGenBank)


for (i in 1:length(files2)){
  assign(paste(paste("df", i, sep="_"), "summary", sep="."), data.frame(genes(files2[[i]])))
  t<-paste(paste("df", i, sep="_"), "summary", sep=".")
  df<-get(t)
  df$seqnames<-paste('g',i,sep='')
  assign(paste(paste("df", i, sep="_"), "summary", sep="."), df)
}

files2<-lapply(ls(pattern='df_*'), get)

gggene_configure<-function(seqname){
  seqname<-select(seqname,seqnames,gene,start,end,strand)
  seqname$gene<-ifelse(is.na(seqname$gene),'hypothetical',seqname$gene)
  seqname$strand<-ifelse(seqname$strand=='+','forward','reverse')
  seqname$direction<-ifelse(seqname$strand =='forward',1,-1)

  return(seqname)
  
}

dfs<-lapply(ls(pattern = 'df_'),get)


all<-bind_rows(dfs)
all2<-gggene_configure(all)
all<-all2
all<-select(all,seqnames,gene,start,end,strand,direction)
names(all)<-c('molecule','gene','start','end','strand','direction')
filenames<-data.frame(filenames)
filenames<-filenames %>% 
  mutate(isolate = map_chr(filenames, function(s) rev(strsplit(s, "_")[[1]])[6])) 
filenames$isolate<-str_replace_all(filenames$isolate,'./oxa/','')
#filenames$isolate<-str_replace_all(filenames$isolate,'.gbk','')
filenames<-select(filenames,-filenames)
filenames$molecule<-paste('g',1:nrow(filenames),sep = '')
all<-left_join(all,filenames,by=c("molecule"="molecule"))
all<-select(all,isolate,gene,start,end,strand,direction)
names(all)<-c('id','gene','start','end','strand','direction')

FP<-filter(flanker_output,window==5000) %>% select(id,cluster) %>% distinct()
names(FP)<-c('id','Flank Pattern')
all<-left_join(all,FP,by=c("id"="id"))
all$gene<-ifelse(all$gene=='bla','blaKPC-2/3',paste('FP',all$`Flank Pattern`,sep=''))





p<-ggtree(tree)


y<-select(x,id)

plasmids<-read_tsv('~/oxa/plasmids') %>% filter(id >=80 & cov >= 80) %>% select(guuid,gene)
pOXA<-filter(plasmids, gene =='IncL/M(pOXA-48)_1_pOXA-48')

pOXA<-pOXA %>% 
  mutate(guuid = map_chr(guuid, function(s) rev(strsplit(s, "_")[[1]])[1])) 

y$`IncL/M(pOXA-48)`<-ifelse(y$id %in% pOXA$guuid,'Present','Absent' )



y$`IncL/M(pOXA-48)`<-as.factor(y$`IncL/M(pOXA-48)`)

mycolors<-c("#FFFFFF" ,"#000000")

p2<-facet_plot(p,panel='L/M(pOXA-48)-type',data=y,geom=geom_tile,aes(x=1,fill=`IncL/M(pOXA-48)`)) + scale_fill_manual(values=mycolors)

p2<-p2 + new_scale_fill()
mycolors <- colorRampPalette(brewer.pal(9, "Set1"))(18)

p3<- p2+geom_facet(panel = 'Alignment',mapping= aes(xmin=start,xmax=end,fill=gene,forward=direction),data = all, geom = geom_motif, on = 'blaKPC-2/3') + scale_fill_manual(values=mycolors,breaks=c("FP1","FP2","FP3","FP3","FP5","FP6","FP7","FP8","FP9","FP10","FP11","FP12","FP13","FP14","FP15","FP16","FP17"),name="Flank Pattern")

flanker_output$window=-1*flanker_output$window
p3<-p3+new_scale_fill()

p4<-facet_plot(p3, panel="Flankergram",data=flanker_output,geom=geom_tile, aes(x=window,fill=group))  + scale_fill_viridis_c(name='Window Cluster')

mlst<-read_csv('~/oxa/mlst.csv')
c<-mlst %>% group_by(mlst) %>% count() %>% filter(n>1)
mlst$mlst<-ifelse(mlst$mlst %in% c$mlst,mlst$mlst,'other')
mlst$mlst<-as.character(mlst$mlst)

p4<-p4 +new_scale_fill()


mycolors <- colorRampPalette(brewer.pal(9, "Set1"))(10)

p5<-facet_plot(p4,panel="MLST",data=mlst,geom=geom_tile,aes(x=1,fill=mlst)) + scale_fill_manual(values=mycolors,name="MLST")


p5<- p5 + theme_bw() +
  xlim_tree(0.08) +
  xlim_expand(c(-5000,0),'Alignment') +
  xlim_expand(c(-5000,0),'Flankergram') + 
  theme(axis.text.y = element_blank(),axis.ticks.y = element_blank()) +
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))



#here we adjust the size of the columns



#have to make mlst/flank panels smaller
gt = ggplot_gtable(ggplot_build(p5))
gtable_show_layout(gt) # will show you the layout - very handy function
gt # see plot layout in table format
gt$layout$l[grep('panel-1-2', gt$layout$name)] # you want to find the column specific to panel-2
gt$widths[7]=0.3*gt$widths[7]


gt$widths[13] = 0.3*gt$widths[13]
grid.draw(gt) # plot with grid draw

```

Here we took a single representative member of each flank pattern (FP) and sketched these using Mash (on default settings). We then performed a mash screen against assemblies of all EUSCAPE isolates and assigned these to the top hit - e.g. mash screen FPs.msh file.fasta | sort -gk1 | tail -1

```{r Screen of EUSCAPE short read data, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

kpc_mash<-read_tsv('./kpc/EUSCAPE/KPC_mash')

                    
meta<-read_tsv('./kpc/EUSCAPE/meta')

kpc_mash<-left_join(kpc_mash,meta,by=c("guuid"="Run accession"))
                                  

kpc_mash<-filter(kpc_mash,!is.na(Country))

t<-table(kpc_mash$Country,kpc_mash$group)
fisher.test(t,simulate.p.value = T)



kpc_mash<-read_tsv('./kpc/EUSCAPE/KPC_mash')

                    
meta<-read_tsv('./kpc/EUSCAPE/meta')

kpc_mash<-left_join(kpc_mash,meta,by=c("guuid"="Run accession"))

kpc_mash<-filter(kpc_mash,!is.na(kpc_mash$`Meropenem MIC (centralised re-testing)`) & `Meropenem MIC (centralised re-testing)` != 'Not tested')

res<-c('32','>32','16') # EUCAST breakpoint in >8 for mero
kpc_mash$R<-ifelse(kpc_mash$`Meropenem MIC (centralised re-testing)` %in% res,'R','S')

t<-table(kpc_mash$R,kpc_mash$group)
fisher.test(t)

tt<-filter(kpc_mash, group=='ENA_CABFYZ010000002_CABFYZ010000002.1_blaKPC-3_1_7200_upstream_flank.fasta' | group=='ENA_CABFZC010000002_CABFZC010000002.1_blaKPC-3_1_7200_downstream_flank.fasta')
t<-table(tt$group,tt$R)
fisher.test(t)

oxa_mash<-read_tsv('./oxa/OXA_2200_hits') %>% select(guuid,cluster)
meta<-read_tsv('./kpc/EUSCAPE/meta')
oxa_mash<-left_join(oxa_mash,meta,by=c("guuid"="Run accession"))
table(oxa_mash$cluster)
t<-oxa_mash<-filter(oxa_mash,!is.na(oxa_mash$`Meropenem MIC (centralised re-testing)`) & `Meropenem MIC (centralised re-testing)` != 'Not tested')




table(oxa_mash$cluster,oxa_mash$`Meropenem MIC (centralised re-testing)`)
table(oxa_mash$cluster)
res<-c('32','>32','16')
oxa_mash$R<-ifelse(oxa_mash$`Meropenem MIC (centralised re-testing)` %in% res,'R','S')
t<-table(oxa_mash$cluster,oxa_mash$R)

oxa_mash$cluster<-str_replace_all(oxa_mash$cluster,'.fasta','')
n<-oxa_mash %>% group_by(oxa_mash$`Meropenem MIC (centralised re-testing)`,cluster) %>% count()
names(n)<-c("mic","cluster","n")
n$mic<-factor(n$mic,levels=c('≤0.06','0.12','0.25','0.5','1','2','4','8','16','32','>32'))

#here is figure S1
FigS1<-ggplot(n) +
  aes(x=cluster,y=mic,size=n) +
  geom_point() +
  xlab('Flank Pattern (FP)') +
  ylab('MIC') + geom_hline(yintercept = 8,linetype='dashed',color='red')
```

```{r Table S2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#here we recreate table S2
flanker_500<-read_csv('./kpc/validation/out_500_blaKPC-3_1_mm')
flanker_500<-flanker_500 %>% 
  mutate(assembly_1 = map_chr(assembly_1, function(s) rev(strsplit(s, "_")[[1]])[6])) 
flanker_5000<-read_csv('./kpc/validation/out_5000_blaKPC-3_1_mm')
flanker_5000<-flanker_5000 %>% 
  mutate(assembly_1 = map_chr(assembly_1, function(s) rev(strsplit(s, "_")[[1]])[6])) 
flanker_output<-kpc_store
flanker_final<-filter(flanker_output,window==7200) %>% distinct() %>% select(guuid,ID) 

mefinder_500<-read_tsv('./kpc/validation/mefinder_500')
mefinder_500<-mefinder_500 %>% 
  mutate(guuid = map_chr(guuid, function(s) rev(strsplit(s, "_")[[1]])[6])) 
mefinder_5000<-read_tsv('./kpc/validation/mefinder_5000')
mefinder_5000<-mefinder_5000 %>% 
  mutate(guuid = map_chr(guuid, function(s) rev(strsplit(s, "_")[[1]])[6])) 
tt500<-read_tsv('./kpc/validation/TETyper_500.txt') %>% select(guuid,cluster)
tt5000<-read_tsv('./kpc/validation/TETyper_5000.txt')  %>% select(guuid,cluster)
tt_all<-read_tsv('./kpc/validation/all_tetyper_full.txt') %>% select(guuid,cluster)

#here we match up tetyper output to everything else

idx <- sapply(tt500$guuid, grep, flanker_500$assembly_1)
tt500$guuid<-flanker_500$assembly_1[idx]


idx <- sapply(tt5000$guuid, grep, flanker_5000$assembly_1)
tt5000$guuid<-flanker_5000$assembly_1[idx]



idx <- sapply(tt_all$guuid, grep, flanker_5000$assembly_1)
tt_all$guuid<-flanker_5000$assembly_1[idx]

#then we do a left join



all<-left_join(flanker_500,flanker_5000,by=c("assembly_1"="assembly_1")) %>% left_join(flanker_final, by=c("assembly_1"="guuid")) %>% left_join(mefinder_500,by=c("assembly_1"="guuid"))%>% left_join(mefinder_5000,by=c("assembly_1"="guuid")) %>% left_join(tt500,by=c("assembly_1"="guuid")) %>% left_join(tt5000,by=c("assembly_1"="guuid")) %>% left_join(tt_all,by=c("assembly_1"="guuid"))

all<-select(all,-cov,-id)

names(all)<-c("guuid","Flanker 500bp","Flanker 5000bp", "Flanker 7200bp","MEFinder 500bp","MEFinder 5000bp","TETyper 500bp","TETyper 5000bp","TETyper Tn4401 whole")

all[is.na(all)]<-"No hits"

#we remove the TETyper snp profile because Flanker analysis (as performed here) does not include the gene
all$`TETyper Tn4401 whole`<-str_replace_all(all$`TETyper Tn4401 whole`,'-.*','')

all %>% 
  kbl() %>% 
  kable_styling
```

